Through the eyes of the teacher

### 2021-11-24 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic-data-script.tex
update demo table

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Through the eyes of the teacher}
\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
\date{}

@@

\hypertarget{state-of-research}{%
\section{State of research}\label{state-of-research}}

Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop (Barnes, 2004). The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching. Learning to develop such classroom management skills and to teach effectively is a complicated and complex process (Wolff, Jarodzka, \& Boshuizen, 2017).

During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events. This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017). Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff, Jarodzka, \& Boshuizen, 2017)

Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff, Jarodzka, \& Boshuizen, 2017). For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students. The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017). Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010). Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).

\hypertarget{research-questions}{%
\subsection{Research questions}\label{research-questions}}

The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions. The disruptions were experimentally varied using a previously written script. Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.

In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster. In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately (Berliner, 2001; Lachner, Jarodzka, \& Nückles, 2016).

@@

For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted. The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance. Participation in the study was voluntary and only took place after written consent has been given.

@@

\caption{\label{tab:demographicspilottable}Demographic Information and Teaching Experience}

@@

\begin{tabular}{lllllllllll}
\toprule
group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{Min age} & \multicolumn{1}{c}{Max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M exp.} & \multicolumn{1}{c}{Min exp.} & \multicolumn{1}{c}{Max exp.} & \multicolumn{1}{c}{SD exp.}\\
\midrule
expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
\bottomrule
\end{tabular}

@@

The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices. Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more (Messner \& Reusser, 2000).

\hypertarget{procedure-data-collection}{%
\subsection{Procedure/ Data collection}\label{procedure-data-collection}}

\hypertarget{set-up}{%
\subsubsection{Set up}\label{set-up}}

For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig. The subjects were divided into groups of four, so the study was conducted on two different sessions. All participants were asked to hold a 10-minute lesson. The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.

One person from the group of 4 acted as a teacher, the other three subjects acted as the class. The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).

The lesson disruptions were displayed as instructions during the lesson for all ``students'' but not the teacher. In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase. In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.

\begin{figure}

{\centering \includegraphics[width=5.94in]{./pictures/datacollection}

\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
\end{figure}

\hypertarget{eyetracking-data}{%
\subsubsection{Eyetracking data}\label{eyetracking-data}}

A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants. The head unit is a measuring device with different sensitive sensors. A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds. Infrared light illuminators support the eye tracking sensors which record the eye orientation. The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second. The scene camera has a field of view of 90 deg. in 16:9 format (82 deg. horizontal and 52 deg. vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height). The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.

\hypertarget{coding-data-preparation-reliability}{%
\subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}

\hypertarget{eyetracking-data-1}{%
\subsubsection{Eyetracking Data}\label{eyetracking-data-1}}

The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson. The software allows for non-screen based recordings of a participants' attention while moving in real-world settings. The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video. In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software. Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data. Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form. Tobii Pro does not allow to do AOI based analyses within Pro Lab. So we exported a tsv. file to do further analyses in the software R.

\hypertarget{gaze-relational-index-gri}{%
\paragraph{Gaze relational index (GRI)}\label{gaze-relational-index-gri}}

The GRI is a measure of visual expertise in information processing. This metric is calculated as the ratio of mean fixation duration to fixation count. The GRI is higher for novices than for experts. (Gegenfurtner et al., 2020)

The first table provides an overview over the

\caption{\label{tab:GRItable1}GRI}

\tiny{

\begin{tabular}{lllllllll}
\toprule
TOI & \multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{DurTOI} & \multicolumn{1}{c}{M Dur Fix} & \multicolumn{1}{c}{Number Fix} & \multicolumn{1}{c}{TimeTOI Dur} & \multicolumn{1}{c}{OldGRI} & \multicolumn{1}{c}{NewGRI}\\
\midrule
Asking question & 01\_04\_C & Novice & 3,869.00 & 2,925.62 & 3.00 & 1.32 & 975.21 & 0.44\\
Asking question & 01\_02\_A & Expert & 7,112.00 & 2,925.62 & 13.00 & 2.43 & 225.05 & 0.19\\
Asking question & 01\_03\_B & Novice & 12,863.00 & 2,925.62 & 4.00 & 4.40 & 731.41 & 1.10\\
Asking question & 01\_01\_D & Expert & 7,648.00 & 2,925.62 & 7.00 & 2.61 & 417.95 & 0.37\\
Asking question & 02\_01\_A & Novice & 7,422.00 & 2,925.62 & 3.00 & 2.54 & 975.21 & 0.85\\
Asking question & 02\_02\_B & Novice & 7,082.00 & 2,925.62 & 9.00 & 2.42 & 325.07 & 0.27\\
Asking question & 02\_03\_C & Novice & 8,045.00 & 2,925.62 & 8.00 & 2.75 & 365.70 & 0.34\\
Asking question & 02\_04\_D & Novice & 6,595.00 & 2,925.62 & 6.00 & 2.25 & 487.60 & 0.38\\
Calibration phase & 01\_04\_C & Novice & 17,224.00 & 12,275.12 & 14.00 & 1.40 & 876.79 & 0.10\\
Calibration phase & 01\_02\_A & Expert & 13,335.00 & 12,275.12 & 10.00 & 1.09 & 1,227.51 & 0.11\\
Calibration phase & 01\_03\_B & Novice & 10,615.00 & 12,275.12 & 17.00 & 0.86 & 722.07 & 0.05\\
Calibration phase & 01\_01\_D & Expert & 16,470.00 & 12,275.12 & 9.00 & 1.34 & 1,363.90 & 0.15\\
Calibration phase & 02\_01\_A & Novice & 17,902.00 & 12,275.12 & 13.00 & 1.46 & 944.24 & 0.11\\
Calibration phase & 02\_02\_B & Novice & 12,325.00 & 12,275.12 & 12.00 & 1.00 & 1,022.93 & 0.08\\
Calibration phase & 02\_03\_C & Novice & 16,494.00 & 12,275.12 & 18.00 & 1.34 & 681.95 & 0.07\\
Calibration phase & 02\_04\_D & Novice & 20,964.00 & 12,275.12 & 14.00 & 1.71 & 876.79 & 0.12\\
Chatting with neighbour & 01\_04\_C & Novice & 9,843.00 & 4,070.12 & 27.00 & 2.42 & 150.75 & 0.09\\
Chatting with neighbour & 01\_02\_A & Expert & 2,607.00 & 4,070.12 & 1.00 & 0.64 & 4,070.12 & 0.64\\
Chatting with neighbour & 01\_03\_B & Novice & 11,060.00 & 4,070.12 & 10.00 & 2.72 & 407.01 & 0.27\\
Chatting with neighbour & 01\_01\_D & Expert & 6,612.00 & 4,070.12 & 3.00 & 1.62 & 1,356.71 & 0.54\\
Chatting with neighbour & 02\_01\_A & Novice & 7,429.00 & 4,070.12 & 5.00 & 1.83 & 814.02 & 0.37\\
Chatting with neighbour & 02\_02\_B & Novice & 8,397.00 & 4,070.12 & 11.00 & 2.06 & 370.01 & 0.19\\
Chatting with neighbour & 02\_03\_C & Novice & 11,713.00 & 4,070.12 & 11.00 & 2.88 & 370.01 & 0.26\\
Chatting with neighbour & 02\_04\_D & Novice & 11,443.00 & 4,070.12 & 4.00 & 2.81 & 1,017.53 & 0.70\\
Clicking pen & 01\_04\_C & Novice & 12,980.00 & 8,809.75 & 4.00 & 1.47 & 2,202.44 & 0.37\\
Clicking pen & 01\_02\_A & Expert & 12,071.00 & 8,809.75 & 20.00 & 1.37 & 440.49 & 0.07\\
Clicking pen & 01\_03\_B & Novice & 26,272.00 & 8,809.75 & 16.00 & 2.98 & 550.61 & 0.19\\
Clicking pen & 01\_01\_D & Expert & 11,597.00 & 8,809.75 & 11.00 & 1.32 & 800.89 & 0.12\\
Clicking pen & 02\_01\_A & Novice & 16,114.00 & 8,809.75 & 11.00 & 1.83 & 800.89 & 0.17\\
Clicking pen & 02\_02\_B & Novice & 9,409.00 & 8,809.75 & 12.00 & 1.07 & 734.15 & 0.09\\
Clicking pen & 02\_03\_C & Novice & 16,269.00 & 8,809.75 & 27.00 & 1.85 & 326.29 & 0.07\\
Clicking pen & 02\_04\_D & Novice & 24,220.00 & 8,809.75 & 19.00 & 2.75 & 463.67 & 0.14\\
Drawing on paper & 01\_04\_C & Novice & 39,979.00 & 34,414.38 & 27.00 & 1.16 & 1,274.61 & 0.04\\
Drawing on paper & 01\_02\_A & Expert & 44,971.00 & 34,414.38 & 87.00 & 1.31 & 395.57 & 0.02\\
Drawing on paper & 01\_03\_B & Novice & 129,708.00 & 34,414.38 & 79.00 & 3.77 & 435.62 & 0.05\\
Drawing on paper & 01\_01\_D & Expert & 74,511.00 & 34,414.38 & 92.00 & 2.17 & 374.07 & 0.02\\
Drawing on paper & 02\_01\_A & Novice & 43,469.00 & 34,414.38 & 31.00 & 1.26 & 1,110.14 & 0.04\\
Drawing on paper & 02\_02\_B & Novice & 147,788.00 & 34,414.38 & 295.00 & 4.29 & 116.66 & 0.01\\
Drawing on paper & 02\_03\_C & Novice & 26,495.00 & 34,414.38 & 46.00 & 0.77 & 748.14 & 0.02\\
Drawing on paper & 02\_04\_D & Novice & 27,915.00 & 34,414.38 & 11.00 & 0.81 & 3,128.58 & 0.07\\
Drumming hands & 01\_04\_C & Novice & 43,507.00 & 11,415.88 & 41.00 & 3.81 & 278.44 & 0.09\\
Drumming hands & 01\_02\_A & Expert & 20,530.00 & 11,415.88 & 27.00 & 1.80 & 422.81 & 0.07\\
Drumming hands & 01\_03\_B & Novice & 12,615.00 & 11,415.88 & 6.00 & 1.11 & 1,902.65 & 0.18\\
Drumming hands & 01\_01\_D & Expert & 23,121.00 & 11,415.88 & 17.00 & 2.03 & 671.52 & 0.12\\
Drumming hands & 02\_01\_A & Novice & 62,326.00 & 11,415.88 & 50.00 & 5.46 & 228.32 & 0.11\\
Drumming hands & 02\_02\_B & Novice & 24,699.00 & 11,415.88 & 25.00 & 2.16 & 456.64 & 0.09\\
Drumming hands & 02\_03\_C & Novice & 27,775.00 & 11,415.88 & 49.00 & 2.43 & 232.98 & 0.05\\
Drumming hands & 02\_04\_D & Novice & 14,998.00 & 11,415.88 & 9.00 & 1.31 & 1,268.43 & 0.15\\
Looking at phone & 01\_04\_C & Novice & 7,984.00 & 11,563.00 & 8.00 & 0.69 & 1,445.38 & 0.09\\
Looking at phone & 01\_02\_A & Expert & 19,897.00 & 11,563.00 & 28.00 & 1.72 & 412.96 & 0.06\\
Looking at phone & 01\_03\_B & Novice & 40,427.00 & 11,563.00 & 30.00 & 3.50 & 385.43 & 0.12\\
Looking at phone & 01\_01\_D & Expert & 32,387.00 & 11,563.00 & 29.00 & 2.80 & 398.72 & 0.10\\
Looking at phone & 02\_01\_A & Novice & 33,557.00 & 11,563.00 & 14.00 & 2.90 & 825.93 & 0.21\\
Looking at phone & 02\_02\_B & Novice & 16,321.00 & 11,563.00 & 19.00 & 1.41 & 608.58 & 0.07\\
Looking at phone & 02\_03\_C & Novice & 28,223.00 & 11,563.00 & 47.00 & 2.44 & 246.02 & 0.05\\
Looking at phone & 02\_04\_D & Novice & 31,944.00 & 11,563.00 & 19.00 & 2.76 & 608.58 & 0.15\\
Putting head on table & 01\_04\_C & Novice & 20,929.00 & 17,049.88 & 38.00 & 1.23 & 448.68 & 0.03\\
Putting head on table & 01\_02\_A & Expert & 23,402.00 & 17,049.88 & 27.00 & 1.37 & 631.48 & 0.05\\
Putting head on table & 01\_03\_B & Novice & 39,159.00 & 17,049.88 & 41.00 & 2.30 & 415.85 & 0.06\\
Putting head on table & 01\_01\_D & Expert & 6,354.00 & 17,049.88 & 4.00 & 0.37 & 4,262.47 & 0.09\\
Putting head on table & 02\_01\_A & Novice & 51,225.00 & 17,049.88 & 45.00 & 3.00 & 378.89 & 0.07\\
Putting head on table & 02\_02\_B & Novice & 11,322.00 & 17,049.88 & 20.00 & 0.66 & 852.49 & 0.03\\
Putting head on table & 02\_03\_C & Novice & 61,713.00 & 17,049.88 & 81.00 & 3.62 & 210.49 & 0.04\\
Putting head on table & 02\_04\_D & Novice & 57,484.00 & 17,049.88 & 42.00 & 3.37 & 405.95 & 0.08\\
Yelling & 01\_04\_C & Novice & 6,083.00 & 889.50 & 1.00 & 6.84 & 889.50 & 6.84\\
Yelling & 01\_02\_A & Expert & 1,995.00 & 889.50 & 1.00 & 2.24 & 889.50 & 2.24\\
Yelling & 01\_03\_B & Novice & 6,527.00 & 889.50 & 1.00 & 7.34 & 889.50 & 7.34\\
Yelling & 01\_01\_D & Expert & 2,245.00 & 889.50 & 1.00 & 2.52 & 889.50 & 2.52\\
Yelling & 02\_01\_A & Novice & 9,105.00 & 889.50 & 7.00 & 10.24 & 127.07 & 1.46\\
Yelling & 02\_02\_B & Novice & 2,548.00 & 889.50 & 5.00 & 2.86 & 177.90 & 0.57\\
Yelling & 02\_03\_C & Novice & 2,992.00 & 889.50 & 2.00 & 3.36 & 444.75 & 1.68\\
Yelling & 02\_04\_D & Novice & 12,416.00 & 889.50 & 1.00 & 13.96 & 889.50 & 13.96\\
\bottomrule
\end{tabular}

\caption{\label{tab:GRItable2}GRI}

\tiny{

\begin{tabular}{lllllllll}
\toprule
Group & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
\midrule
Expert & Asking question & 2,108.50 & 10.00 & 7,380.00 & 231.70 & 98.30 & 0.39 & 0.18\\
Expert & Calibration phase & 12,283.00 & 9.50 & 14,902.50 & 1,296.54 & 96.50 & 0.13 & 0.03\\
Expert & Chatting with neighbour & 1,829.00 & 2.00 & 4,609.50 & 1,219.33 & 862.20 & 1.32 & 0.16\\
Expert & Clicking pen & 5,416.50 & 15.50 & 11,834.00 & 381.62 & 156.68 & 0.15 & 0.06\\
Expert & Drawing on paper & 25,514.50 & 89.50 & 59,741.00 & 285.30 & 11.27 & 0.03 & 0.01\\
Expert & Drumming hands & 8,405.00 & 22.00 & 21,825.50 & 402.85 & 129.48 & 0.13 & 0.05\\
Expert & Looking at phone & 8,484.50 & 28.50 & 26,142.00 & 297.79 & 7.39 & 0.11 & 0.03\\
Expert & Putting head on table & 7,605.50 & 15.50 & 14,878.00 & 1,091.53 & 1,145.29 & 0.16 & 0.07\\
Expert & Yelling & 580.00 & 1.00 & 2,120.00 & 580.00 & 0.00 & 3.66 & 0.30\\
Novice & Asking question & 3,198.00 & 5.50 & 7,646.00 & 703.26 & 320.81 & 0.51 & 0.30\\
Novice & Calibration phase & 12,272.50 & 14.67 & 15,920.67 & 853.95 & 130.15 & 0.09 & 0.03\\
Novice & Chatting with neighbour & 4,817.17 & 11.33 & 9,980.83 & 617.28 & 384.64 & 0.26 & 0.18\\
Novice & Clicking pen & 9,940.83 & 14.83 & 17,544.00 & 955.00 & 774.90 & 0.15 & 0.09\\
Novice & Drawing on paper & 37,381.00 & 81.50 & 69,225.67 & 1,233.52 & 1,156.72 & 0.04 & 0.02\\
Novice & Drumming hands & 12,419.50 & 30.00 & 30,986.67 & 791.90 & 760.35 & 0.10 & 0.04\\
Novice & Looking at phone & 12,589.17 & 22.83 & 26,409.33 & 747.59 & 459.89 & 0.10 & 0.05\\
Novice & Putting head on table & 20,198.00 & 44.50 & 40,305.33 & 535.53 & 252.70 & 0.04 & 0.02\\
Novice & Yelling & 992.67 & 2.83 & 6,611.83 & 635.78 & 409.08 & 4.76 & 4.60\\
\bottomrule
\end{tabular}

\caption{\label{tab:GRItable3}GRI}

\tiny{

\begin{tabular}{llllllll}
\toprule
Group & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
\midrule
Expert & 8,025.17 & 21.50 & 18,159.17 & 1,953.05 & 2,871.09 & 0.16 & 0.08\\
Novice & 12,645.43 & 25.33 & 24,958.93 & 1,878.32 & 2,902.64 & 0.13 & 0.15\\
\bottomrule
\end{tabular}

\caption{\label{tab:calibration phase TOI}Number and Duration (in msec) of Fixations during calibration}

\scriptsize{

\begin{tabular}{lllllll}
\toprule
Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 9.00 & 14,372.00 & 1,597.00 & 16,470.00 & 177.44\\
01\_02\_A & Expert & 10.00 & 10,194.00 & 1,019.00 & 13,335.00 & 101.90\\
01\_03\_B & Novice & 17.00 & 9,234.00 & 543.00 & 10,615.00 & 31.94\\
01\_04\_C & Novice & 14.00 & 15,311.00 & 1,094.00 & 17,224.00 & 78.14\\
02\_01\_A & Novice & 13.00 & 5,157.00 & 397.00 & 17,902.00 & 30.54\\
02\_02\_B & Novice & 12.00 & 10,654.00 & 888.00 & 12,325.00 & 74.00\\
02\_03\_C & Novice & 18.00 & 14,151.00 & 786.00 & 16,494.00 & 43.67\\
02\_04\_D & Novice & 14.00 & 19,128.00 & 1,366.00 & 20,964.00 & 97.57\\
\bottomrule
\end{tabular}

\caption{\label{tab:Calib end to lession start TOI}Number and Duration (in msec) of Fixations Calibration End to Lesson Start}

\scriptsize{

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\title{Through the eyes of the teacher}
\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, Eye-Tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\hypertarget{packages}{%
\section{Packages}\label{packages}}

@@

@@

\caption{\label{tab:demographicstable}Demographic Information and and Teaching Experience}

@@

\begin{tabular}{lllllllllll}
\toprule
Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M Age} & \multicolumn{1}{c}{Min Age} & \multicolumn{1}{c}{Max Age} & \multicolumn{1}{c}{SD Age} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{SD Exp.}\\
\midrule
Expert & 4 & 7.00 & 49.25 & 27.00 & 59.00 & 14.93 & 25.25 & 3.00 & 37.00 & 15.20\\
Novice & 11 & 18.00 & 23.18 & 21.00 & 25.00 & 1.08 & 0.55 & 0.00 & 6.00 & 1.81\\
\bottomrule
\end{tabular}

@@

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}
